
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Divyasha Agrawal} % Your name
\address{divyasha.agrawal@gmail.com} % email
\address{github.com/DivyashaAgrawal \\ linkedin.com/divyasha-agrawal}
\address{Patna ,Bihar \\ (+91) 8789623763} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Vellore Institute of Technology, Vellore} \hfill {\em July 2015 - 2019} 
\\ Bachelor of Technology, Computer Science and Engineering \hfill { CGPA: 8.53/10} 
\\ 
\\
{\bf D.A.V Public School,Patna}  \hfill{\em May 2015}
\\High School (Physics, Chemistry and Mathematics) \hfill {GPA: 89.6/100}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Basic:  &  CSS3 ,HTML, MySQL, mongoDB \\
Intermediate & Data Structures, OOP , C, C++, Python \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf BOSCH, RBEI, Bangalore} \textit{Project Trainee}\hfill {\em Dec 2018 - Present}
\begin{itemize}
\item Working with the team on Project sparkIT-A developer's test suite.
\item Analyzed and extracted sequence Diagrams made on Enterprise architecture using openCV and python.
\\ Using NLP techniques to analyze and extract information and diagrams from concept and design documents.
\end{itemize}
\\
\\
{\bf Amazon ACMS} \textit{Student under mentor-ship}\hfill {\em Feb 2018 - Jun 2018}
\begin{itemize}
\item Worked under a mentor and came up with a design  of Image recommendation system
\item Developed the system for social media which will fetch top 10 images for the user most likely get likes and reactions.
\end{itemize}
\\
\\
{\bf TATA Communications, New Delhi} \textit{Intern}\hfill {\em Jun 2017}
\begin{itemize}
\item Researched on current malware Outburst and IBM BigFix and developed spreadsheets for risk analysis on system network and how to fix it. 
\end{itemize}
\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects} \itemsep -2pt
{\bf Speech Recognition and formation } \hfill {\em Aug 2018 - Oct 2018} 
\\ This project takes past speeches of a political figure and creates or forms new speeches of that personality. Used python and NLTK.
\\
\\
{\bf CAPTCHA Recognition} \hfill {\em Jan 2018 - Mar 2018}
\\ This project uses multi-layer perceptron classifier to recognize CAPTCHA from university website. Used python, sklearn, and OpenCV 
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certification}

{\bf Machine Learning} by Stanford University (Coursera)  \hfill {\em Apr 2018}
\\
{\bf Fundamentals of Digital Image processing} by Northwestern University(Coursera)  \hfill {\em Sep 2017}
\end{rSection}

\end{document}
